---
title: "Pregnancy Data"
author: "Elaine Zhang"
format: html
execute: 
  echo: false
---

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(tidybayes)
library(brms)
library(gtsummary)
library(broom.mixed)
```

```{r}
my_data <- read.csv("pregnancy-data.csv", sep = ",")

#turning the csv into a table and selecting for mental health variables. Got rid of data with missing values and renamed EPDS
my_table <- tibble(my_data) |>
  select(PROMIS_Anxiety, Edinburgh_Postnatal_Depression_Scale, Threaten_Baby_Danger, Birth_Weight) |>
  drop_na() |>
  rename(EPDS = Edinburgh_Postnatal_Depression_Scale)
```

```{r}
#| cache: true

fit_my_data <- brm(
  formula = Birth_Weight ~ PROMIS_Anxiety + EPDS + Threaten_Baby_Danger,
  data = my_table,
  family = gaussian,
  silent = 2,
  refresh = 0,
  seed = 12
)
```
Mental well-being has changed drastically during COVID-19, which may have effects on children born during this period due to the epigenetic alterations. It is shown that mothers with a high Edinburgh Postnatal Depression Scale (EPDS) results have children weighing 0-8% less compared to the average weight of 3,463 grams. Using data from a 2024 study, I seek to find a correlation between maternal mental health and health of the baby during COVID-19. I modeled a linear relationship of the EPDS results, ranging from integers 0-30, and baby mass in grams.
```{r}
#| warning: false

new_data <- tibble(EPDS = seq(min(my_table$EPDS), max(my_table$EPDS), length.out = 100),
                   PROMIS_Anxiety = mean(my_table$PROMIS_Anxiety),
                   Threaten_Baby_Danger = mean(my_table$Threaten_Baby_Danger))
# Add predicted draws
predicted_draws <- fit_my_data %>%
  add_epred_draws(newdata = new_data)

# Plot the effect of EPDS on Birth Weight
predicted_draws %>%
  ggplot(aes(x = EPDS, y = .epred)) +
  stat_lineribbon() +
  labs(title = "Effect of Postnatal Depression on Baby Weight",
       x = "Edinburgh Postnatal Depression Scale Score",
       y = "Predicted Baby Weight",
       caption = "Public Data by Yeganeh Bavafa under \n\"Mental health in the pregnancy during the COVID-19\"",
       level = "Level") +
  theme_minimal()
```

```{r}
tbl_regression(fit_my_data, intercept = TRUE)
```

